 
\documentclass[letterpaper, 12pt]{letter}
\usepackage{times, fullpage}
\usepackage{url}

\address{Department of Biological Sciences\\Flint and Main\\Texas Tech University\\
  Lubbock, TX 79409}

\name{Dylan W. Schwilk}

\begin{document}
\begin{letter}{}

\opening{Dear Dr. David Gibson,}

Enclosed is our revised manuscript research article, ``Moisture absorption and
drying alter nonadditive litter flammability in a mixed conifer forest''.

We have made all changes suggested. I've itemized our replies below. I must agree that the editors were correct, the combined figures are an improvement. Thank you.

\begin{quote}
The authors made some progress towards putting relatively less emphasis on
single species treatments compared to mixture effects. But I still feel that
two figures for single taxa is too many. It should be easy to combine Fig. 1
and 2 into one 5-panel figure. The two panels for spread rate and fuel consumed
could then be next to one another. That some panels have five and others four
taxa is not a problem since the legends with taxa are in the figures
themselves.

I also recommend combining Figures 4 and 5 to save a bit more journal space.
These figures have very similar layout and only differ in the variable on the
y-axis.
\end{quote}

We have combined Figs. 1 and 2 into a single figure aligned as suggested (new Fig. 1). We have also combined and stacked Figs. 4 and 5 as new Fig. 3.

\begin{quote}
  Point 5 in Abstract: write nonadditive as one word --- without hyphen to be
  consistent with the rest of the text – please check that you use nonadditive or
  non-additive consistently throughout
\end{quote}

Dang, I managed to introduce these errors in R2. Fixed now.

\begin{quote}
Point 5 in Abstract: typo in mixture
\end{quote}fam


Fixed.

\begin{quote}
  Line 137: ``estimation of the mixture effect on the dry-down process''?
\end{quote}

Thank you, edited.

\begin{quote}
  L332: provide a reference for this statement
\end{quote}

Done.

\begin{quote}
References: Blauw et al ref --- typo in Ecology and Evolution
Cornwell et al, Zhao et al and Grootemaat et al references: initials of van Logtestijn are R.S.P, of Cornelissen J.H.C. Please double-check other references for correctness as well.
\end{quote}

My apologies and thank you! The citations were correct in the source bibliography file, but there is a bug in the bibtex style that I used to make the PDF. I've gone through and checked other citations for the same issue with multiple middle names and I re-coded names in the source bibliography file as a workaround. This bug affected several entries where the style jettisoned initials for authors with multiple middle initials. I will include all source files with the submission.


\closing{Sincerely,}

\end{letter}
\end{document}
