 
\documentclass[letterpaper, 12pt]{letter}
\usepackage{times, fullpage}
\usepackage{url}

\address{Department of Biological Sciences\\Flint and Main\\Texas Tech University\\
  Lubbock, TX 79409}

\name{Dylan W. Schwilk}

\begin{document}
\begin{letter}{}

\opening{Dear Dr. David Gibson,}

Enclosed is our revised manuscript research article, ``Moisture absorption and
drying alter nonadditive litter flammability in a mixed conifer forest''.

I understand that the figure captions require more detail so that they stand
alone. I've itemized our replies below. There are only four areas of change to
the text: a citation for the Jepson Flora Project to accurately cite taxonomic
authorities (lines 166-167), the new Table 1, the caption for Fig. 1, and the
sentences at lines 135-138.

\begin{quote}
  Figure 1a. The legend says 8 species, but there are 7 lines - presumably 2-3
per genera except just one for Quercus (Q. kelloggii). Should there be 3 lines
for Pinus? The underlying species need distinguishing or at least explaining.
\end{quote}

There are, in fact, eight lines in the figure. However, the lines for \emph{P. ponderosa} and \emph{P. jeffreyi} overlap quite closely and are difficult to distinguish. I played around with line widths and also tried stretching the height of the whole figure, but was unconvinced that this could be improved. Therefore, I've now explained the overlap in the caption so that a reader will not wonder about a missing line.
  

\begin{quote}
  Fig 1 b-e. The legend needs to state that species within genera/family have
been fitted together, except Fig 1c where P. lambertiana is shown separately
from Pinus (P. jeffreyi and P. ponderosa?). The legend for panel C does say,
"Curves indicate best fit beta regression lines by taxonomic group" but this
presumably applies to other panels in various ways with the underlying species
named somewhere.
\end{quote}

Only the captions for 1B and 1C indicated the taxonomic grouping. We've added similar information for 1D and 1E and
also made a new table (Table 1) to allow the reader to quickly see the
groups. We've edited this caption and referenced new Table 1 from the caption.


\begin{quote}
Line 137 and surrounding lines 135-138. The edit still doesn't clarify what is
a much too long a sentence. I suggest breaking it into two. ``There is some
evidence for nonadditive flammability in moist fuels with a single study
finding increasing nonadditivity with moisture (Blauw et al 2015). However,
this study did not include estimation of mixture effects on the dry-down
process and had an unclear relationship to fire behavior in the field''.
\end{quote}

We've made the change as suggested.


\closing{Sincerely,}

\end{letter}
\end{document}
